Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-07-10 paper/scheduler.tex
Implement on-off-on-off-on constraint (i.e spread)
Prevent on-off-on-off-on type of assignments to improve spread of blocks
for a given clinician. Document in more detail in pdf.
Implement a constraint to spread out weekends
Instead of preventing consecutive weekend assignments (X_i + X_{i+1} <= 1),
restrict to a single possible weekend assignment in the span of 4 weekends
(X_i + X_{i+1} + X_{i+2} + X_{i+3} <= 1). This constraint provides a better
spread of weekend assignments.

\subsection{Constraints} \label{constraints}
	\begin{itemize}
		\item Each division needs to have exactly one clinician that covers any given block
			\begin{equation}
				\sum_{c} X_{c, b, d} = 1 \text{ for each } b, d
			\end{equation}
		\item Every weekend needs to have exactly one clinician that covers it
			\begin{equation}
				\sum_{c} Y_{c, w} = 1 \text{ for each } w
			\end{equation}
		\item In a given division, each clinician can only work between the minimum and maximum number of weeks they are allowed (note: these may be different for different divisions)
			\begin{equation}
				m_{c, d} \leq \sum_{d} X_{c, b, d} \leq M_{c, d} \text{ for each } c, d
			\end{equation}
		\item Weekends should be roughly equally distributed between clinicians.
			\begin{equation}
				\floor*{ \frac{W}{C} } \leq \sum_{w} Y_{c, w} \leq \ceil*{ \frac{W}{C} } \text{ for each } c
			\end{equation}
		\item Long weekends should be roughly equally distributed between clinicians.
			\begin{equation}
				\floor*{\frac{|\mc{L}|}{C}} \leq \sum_{w \in \mc{L}} Y_{c, w} \leq \ceil*{\frac{|\mc{L}|}{C}} \text{ for each } c
			\end{equation}
		\item A clinician cannot work two consecutive blocks (across all divisions)
			\begin{equation}
				\sum_d \left(X_{c, b, d} + X_{c, b+1, d}\right) \leq 1 \text{ for each $c$ and each $b \leq B - 1$}
			\end{equation}
		\item A clinician cannot work two consecutive weekends
			\begin{equation}
				Y_{c, w} + Y_{c, w+1} \leq 1 \text{ for each $c$ and each $w \leq W - 1$}
			\end{equation}
	\end{itemize}

>>>>

\subsection{Constraints} \label{constraints}
	\begin{itemize}
		\item Each division needs to have exactly one clinician that covers any given block
			\begin{equation}
				\sum_{c} X_{c, b, d} = 1 \text{ for each } b, d
			\end{equation}
		\item Every weekend needs to have exactly one clinician that covers it
			\begin{equation}
				\sum_{c} Y_{c, w} = 1 \text{ for each } w
			\end{equation}
		\item In a given division, each clinician can only work between the minimum and maximum number of weeks they are allowed (note: these may be different for different divisions)
			\begin{equation}
				m_{c, d} \leq \sum_{d} X_{c, b, d} \leq M_{c, d} \text{ for each } c, d
			\end{equation}
		\item Weekends should be roughly equally distributed between clinicians.
			\begin{equation}
				\floor*{ \frac{W}{C} } \leq \sum_{w} Y_{c, w} \leq \ceil*{ \frac{W}{C} } \text{ for each } c
			\end{equation}
		\item Long weekends should be roughly equally distributed between clinicians.
			\begin{equation}
				\floor*{\frac{|\mc{L}|}{C}} \leq \sum_{w \in \mc{L}} Y_{c, w} \leq \ceil*{\frac{|\mc{L}|}{C}} \text{ for each } c
			\end{equation}
		\item A clinician cannot work two consecutive blocks (across all divisions)
			\begin{equation}
				\sum_d \left(X_{c, b, d} + X_{c, b+1, d}\right) \leq 1 \text{ for each $c$ and each $b \leq B - 1$}
			\end{equation}
		\item Prevent on-off-on-off-on block assignments (across all divisions) to improve the spread of assignments for any given clinician
			\begin{equation}
				\sum_d \left(X_{c, b, d} + X_{c, b + 2, d} + X_{c, b + 4, d}\right) \leq 2 \text{ for each $c$ and each $b \leq B - 4$}
			\end{equation}
		\item Improve spread of weekend assignments by preventing more than 1 assignment for a given clinician in a span of 4 weekends
			\begin{equation}
				Y_{c, w} + Y_{c, w+1} + Y_{c, w+2} + Y_{c, w+3} \leq 1 \text{ for each $c$ and each $w \leq W - 3$}
			\end{equation}
	\end{itemize}
